\begin{center}
\textbf{\huge ACKNOWLEDGEMENT}
\end{center}
\vspace{0.5cm}

First and foremost, I would like to express my immerse gratitude to my advisor Professor, Prof. Bob Hirosky, for his continual guidance and support throughout the last 4 years for me. He guided me into the world of experimental particle physics and fascinated me with his physics insight and technical skills. 

I would also like to express my gratitude to Hengne Li, the former post-doctor in our group who now works as a professor at South China Normal University. His dedication to research has always been an invaluable source of inspiration to me. 

Moreover, I appreciate the efforts from the members of my defense committee, including Dr. Brad Cox, Dr. P.Q. Hung and Dr. Nitya Kallivayalil, for their time reviewing my research, providing precious comments and questions for my thesis, and approving my dissertation.

In addition, I am grateful to the physicists I worked with and learnt from during my 2 years' stay at CERN, such as Tote Hughes and Andrew Whitbeck in the HCAL Phase I upgrading team, Mario Galanti and Josh Kunkle in the HCAL Operation team, Thomas Peiffer and Vieri Candelise in the B2G MC Production team, and many more amazing researchers in the collaboration. 

Finally, I could not have achieved this without the encouragement and love from my parents. I am grateful to my mother Cailing Hu and father Zhiping Wang for supporting me along the way.
\vspace{0.5cm}
\begin{flushleft}
Yanchu Wang

Charlottesville, VA

April, 2019
\end{flushleft}
\newpage
